---
title: "Lab 5"
author: "Anthony Luna"
date: "10/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objectives:

 - Getting counts for different groups
 - use {luridate} to parse dates
 - Find confidence intervals & do t-tsts with t.test()
 - Heatmap with geom_tile()
 
 
```{r, include=FALSE}
library(tidyverse)
library(here)
library(janitor)
```

```{r}
# Import Lobster Data

lobster_abundance <- read_csv(here("data","lobster_abundance.csv"), na="-99999") %>% 
  clean_names()


```

Time to learn something new: Use the dplyr::uncount() unction to expand a frequency variable

```{r}
lobster_tidy <- lobster_abundance %>% 
  uncount(lobster_count)
```

```{r}
ggplot(data = lobster_tidy, aes(x=site, y=size_mm)) +
  geom_jitter(aes(color = site,
                  width = 0.2))


ggplot(data = lobster_tidy, aes(x=site, y=size_mm)) +
  geom_violin(aes(color = site))


ggplot(data = lobster_tidy, aes(x=size_mm)) +
geom_histogram(aes(fill = site)) +
  facet_wrap(~site,scales = "free")
ggplot(data = lobster_tidy) +
geom_qq(aes(sample = size_mm)) +
  facet_wrap(~site,scales = "free")
```

Use `lubridate` to parse dates and times:

I'm going to add a new column with `mutate()`

```{r}
lobster_date <- lobster_tidy %>% 
  mutate(
    date_new = lubridate::mdy(date)
    )
```

Parse 'Date' Column to get the differenct pieces (month, year) separated...

```{r}
lobster_parse_date <-  lobster_date %>% 
  mutate(
    obs_month = lubridate::month(date_new, label = TRUE),
    obs_year = lubridate::year(date_new)
  )
```

Count Lobsters by different groupings
Lets say, I want to count the number of lobsters by year and month
```{r}
lobster_ym <-  lobster_parse_date %>% 
  count(obs_year, obs_month)

lobster_ysite <-  lobster_parse_date %>% 
  count(obs_year,site)

lobster_site <-  lobster_parse_date %>% 
  count(site)

lobster_summary <- lobster_parse_date %>% 
  group_by(site) %>% 
  summarise(
    mean_size = mean(size_mm, na.rm = TRUE),
    sd_size = sd(size_mm, na.rm = TRUE),
    sample_n = n()
    )
```

## Confidence Intervals and t-tests

`t.test()` function is used to find confidence intervals and perorm t-tests

```{r}
ivee_lobsters <- lobster_tidy %>% 
  filter(site == "IVEE") %>% 
  pull(size_mm)

t.test(ivee_lobsters)
```

```{r}
napl_lob <- lobster_parse_date %>% 
  filter(site=="NAPL") %>% 
  pull(size_mm)
mohk_lob <- lobster_parse_date %>% 
  filter(site=="MOHK") %>% 
  pull(size_mm)

t <- t.test(napl_lob,mohk_lob)
```

$`r t$parameter`$


```{r}
lob_2 <- lobster_tidy %>% 
  filter(site %in% c("NAPL","MOHK"))

TTEST_2 <- t.test(size_mm ~site, lob_2)

```


Now to make a geom_tile() heatmap

```{r}
ggplot(data = lobster_ysite, aes(x = obs_year, y=site))+
  geom_tile(aes(fill=n))
```


